---
title: "Summary for different set sizes"
author: "CLETZ Laura"
date: "2025-05-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In order to evaluate and visualize the sizes obtained via the different calibration methods, we need the following packages:
```{r}
library(jsonlite)
library(dplyr)
library(ggplot2)
```

We also need two JSON files that can be downloaded from *Zenodo*:
```{r}
#download.file("https://zenodo.org/records/15355864/files/expert_processed.json?download=1", destfile = 'data/expert_processed.json')
#download.file("https://zenodo.org/records/15441471/files/expert_score2.json?download=1", destfile = 'data/expert_score2.json')

processed_exp <- fromJSON('data/expert_processed.json')
test_set <- fromJSON('data/expert_scores2.json')
```

We are only interested in the (number of) probabilities from the test set:
```{r}
processed_exp <- processed_exp[names(processed_exp) %in% names(test_set)]
proba_list <- lapply(processed_exp, function(df) df$proba)
```

## Size of final set of labels for each methods
We have set our $\alpha$ at 0.05 since we are interested in a 95% coverage.

The quantile for the method "s1 + non-experts" is 0.9990 then:
```{r}
size_1 <- sapply(proba_list, function(p) sum(p > 1-0.9990))
```

The quantile for the method "s1 + experts" is 0.9649 then:
```{r}
size_2 <- sapply(proba_list, function(p) sum(p > 1-0.9649))
```

The quantile for the method "s2 + non-experts" is 0.9990, then:
```{r}
size_3 <- sapply(proba_list, function(p) sum(p > 1-0.9990))
```

The quantile for the method "s2 + experts" is 0.7932, then:
```{r}
size_4 <- sapply(proba_list, function(p) sum(p > 1-0.7932))
```

## Summaries 
```{r}
summary(size_1)
```

```{r}
summary(size_2)
```

```{r}
summary(size_3)
```

```{r}
summary(size_4)
```

# Barplots 
```{r}
size_1_df <- data.frame(count = unname(size_1))

ggplot(size_1_df, aes(x = count)) +
  geom_histogram(binwidth = 1, fill = '#b4a7d5ff', color = 'white') +
  labs(
    title = 'Méthode "s1 + non-experts"',
    x = "Taille de l'ensemble",
    y = "Nombre d'observations"
  ) +
  theme_minimal(base_size = 14)
```

```{r}
size_2_df <- data.frame(count = unname(size_2))

interest_values <- size_2_df %>%
  count(count) %>%
  filter(count > 8 | count == 1)

ggplot(size_2_df, aes(x = count)) +
  geom_histogram(binwidth = 1, fill = '#b4a7d5ff', color = 'white') +
  geom_text(
    data = interest_values,
    aes(x = count, y = n, label = n),
    vjust = -0.5,
    size = 4
  ) +
  labs(
    title = 'Méthode "s1 + experts"',
    x = "Taille de l'ensemble",
    y = "Nombre d'observations"
  ) +
  theme_minimal(base_size = 14)
```

```{r}
size_3_df <- data.frame(count = unname(size_3))

ggplot(size_3_df, aes(x = count)) +
  geom_histogram(binwidth = 1, fill = '#b4a7d5ff', color = 'white') +
  labs(
    title = 'Méthode "s1 + non-experts"',
    x = "Taille de l'ensemble",
    y = "Nombre d'observations"
  ) +
  theme_minimal(base_size = 14)
```


```{r}
size_4_df <- data.frame(count = unname(size_4))

interest_values <- size_4_df %>%
  count(count) %>%
  filter(count != 2)

ggplot(size_4_df, aes(x = count)) +
  geom_histogram(binwidth = 1, fill = '#b4a7d5ff', color = 'white') +
  geom_text(
    data = interest_values,
    aes(x = count, y = n, label = n),
    vjust = -0.5,
    size = 4
  ) +
  labs(
    title = 'Méthode "s2 + experts"',
    x = "Taille de l'ensemble",
    y = "Nombre d'observations"
  ) +
  theme_minimal(base_size = 14)
```