---
title: "AI files merger"
author: "CLETZ Laura"
date: "2025-03-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In order to merge/cross the datas from the JSON files beginning with *ai*, we need the following R packages :
```{r}
library(jsonlite)
library(tibble)
```

## Data processing

Let's read the JSON files as DataFrames and rename the columns for easier merging.
```{r}
# (observation ID + predicted class ID)
ai_answers <- fromJSON("data/ai_answers.json")
ai_answers_df <- data.frame(matrix(unlist(ai_answers), byrow = TRUE), stringsAsFactors = FALSE) |>
  rownames_to_column(var = "obs_id")
colnames(ai_answers_df) <- c("obs_id", "plant_id")

# (name of predicted class + predicted class ID)
ai_classes <- fromJSON("data/ai_classes.json")
ai_classes_df <- do.call(rbind, lapply(ai_classes, as.data.frame)) |>
  rownames_to_column(var = "plant_class")
colnames(ai_classes_df) <- c("plant_class", "plant_id")

# (observation ID + score for #1 predicted class)
ai_scores <- fromJSON("data/ai_scores.json")
ai_scores_df <- data.frame(matrix(unlist(ai_scores), byrow = TRUE), stringsAsFactors = FALSE) |>
  rownames_to_column(var = "obs_id")
colnames(ai_scores_df) <- c("obs_id", "score")
```

We will use the RStudio base' function *merge* instead of the ones available through *dplyr* package.
```{r}
merged_df <- merge(ai_scores_df, ai_answers_df)
merged_all <- merge(merged_df, ai_classes_df)
```

The result will be saved as another JSON file. The file's name ends with "*ai*", this way we know it has been created using *ai* datas.
```{r}
write_json(merged_all, 'data/merged_ai.json', pretty=TRUE)
```