---
title: "Samples Merging"
author: "CLETZ Laura"
date: "2025-03-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In order to merge the datas from the JSON and TxT files, we need the following R packages:
```{r}
library(jsonlite)
library(dplyr)
library(purrr)
library(tidyr)
library(tibble)
```

## Tasks and samples

Let's read the JSON files as DataFrames and rename the columns for easier splitting and merging. 
```{r}
tasks <- fromJSON("data/tasks.json")
tasks_df <- data.frame(
  plant_swe_id = sapply(tasks, function(x) x[[1]]),
  stringsAsFactors = FALSE
)
tasks_df <- rownames_to_column(tasks_df, var = "plantnet_id")

samples <- fromJSON("data/samples.json")
samples$file <- sub("\\.json$", "", samples$file)
```

We *unnest* the columns "name", "id" and "score" from *samples* because most of them contain vectors or lists.
```{r}
samples <- samples %>%
  rowwise() %>%
  mutate(
    min_len = min(length(name), length(id), length(score)),
    name = list(name[1:min_len]),
    id = list(id[1:min_len]),
    score = list(score[1:min_len])
  ) %>%
  mutate(
    name = list(purrr::map(name, function(.x){if (!is.list(.x)) list(.x) else .x})),
    id = list(purrr::map(id, function(.x){if (!is.list(.x)) list(.x) else .x})),
    score = list(purrr::map(score, function(.x){if (!is.list(.x)) list(.x) else .x}))
  ) %>%
  select(-min_len) %>%
  unnest(cols = c(name, id, score))
```

After the *tasks* and *samples* DataFrames are merged, we *nest* the previously unnested columns and save the merged datas in a JSON file.
```{r}
merged_df <- merge(tasks_df, samples, by.x = 'plantnet_id', by.y = 'file')

merged_df <- merged_df %>%
  nest(.by = c("plantnet_id", "plant_swe_id")) %>%
  mutate(
    name  = map(data, "name"),
    id    = map(data, "id"),
    score = map(data, "score")
  ) %>%
  select(-data)

write_json(merged_df, 'data/merged_samples.json', pretty=TRUE)
```

## Ground truth

The *ground_truth.txt* file lists the observations made by the 98 experts, we want to read the lines corresponding to the experts only and save in a JSON file.
```{r}
ground_truth <- read.table("data/ground_truth.txt")
ground_truth <- rownames_to_column(ground_truth)
ground_truth <- ground_truth[which(ground_truth[,2] != -1),]
colnames(ground_truth) <- c('obs_id', 'plantswe_id')
write_json(ground_truth, "data/ground_truth.json", pretty = TRUE)
file.remove('data/ground_truth.txt')
```

Let's then merge our previous merged datas with the experts' truth and save the result in a JSON file.
```{r}
merged_truth <- merge(merged_df, ground_truth, by.x = 'plant_swe_id', by.y = 'plantswe_id')
merged_truth <- merged_truth[!duplicated(merged_truth$plant_swe_id), ]

write_json(merged_truth, 'data/merged_truth.json', pretty=TRUE)
```